---
title: "GSE132880_Healthy_Adult"
author: "Cass Li"
date: "04/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
div.teal pre { background-color:#fff44f; }
div.teal pre.r { background-color:#b2d8d8; }
</style>

<div class = "teal">
```{r library_loading, message = FALSE, warning = FALSE}
# load libraries
library(Seurat)
library(ggplot2)
library(homologene)
library(clustree)
library(dplyr)
library(topGO)
library(org.Mm.eg.db)
library(scales)
library(GSEABase)
library(AUCell)
library(plotly)
library(scran)
```
</div>

Our data.

### Step 1 Load datasets for Healthy.

<div class = "teal">
```{r cache = TRUE}
Healthy_rep1_data <-  Read10X(data.dir = "~/Documents/Project_scRNA_seq_meta_analysis/MetaAnalysis/RawFiles/GSE132880/Healthy227_out/filtered_gene_bc_matrices/mm10/")
Healthy_rep1 <- CreateSeuratObject(Healthy_rep1_data, project = "Healthy_rep1", assay = "RNA", min.cells = 3, min.features = 200)
Healthy_rep1 <- RenameCells(object = Healthy_rep1, new.names = paste0("Healthy_rep1_", Cells(x = Healthy_rep1)))
Healthy_rep1[["percent.mt"]] <- PercentageFeatureSet(Healthy_rep1, pattern = "^mt-")
# fix the metadata
Healthy_rep1@meta.data$age <- "Healthy"
Healthy_rep1@meta.data$species <- "Mouse"
Healthy_rep1@meta.data$rep_no <- 1
# Visualise QC metrics
png(filename = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/Healthyrep1QC.png", width = 600, height = 400)
VlnPlot(Healthy_rep1, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.2)
dev.off()
# Filtering of each dataset is based on the same cut off
Healthy_rep1 <- subset(Healthy_rep1, subset = nFeature_RNA > 200 & nFeature_RNA < 4000 & percent.mt < 20)
# Calculate cell cycle scores - these are human genes and can't be used directly. Use homologene package to solve the problem
s.genes <- human2mouse(cc.genes$s.genes) # return a dataframe
g2m.genes <- human2mouse(cc.genes$g2m.genes) # return a dataframe
Healthy_rep1 <- NormalizeData(Healthy_rep1) # normalise before cell cycle score
Healthy_rep1 <- CellCycleScoring(Healthy_rep1, s.features = s.genes$mouseGene, g2m.features = g2m.genes$mouseGene, set.ident = TRUE) # need to remove Nek2 from the g2m gene list as it's not in any of the datasets. Error still occurs when running it and try the solution in the issue #1227 solution by running a normalisation step first and it works!!
# Use scTransform to normalise datasets
Healthy_rep1 <- SCTransform(Healthy_rep1, vars.to.regress = c("percent.mt", "S.Score", "G2M.Score")) # default assay is now set to SCT

Healthy_rep2_data <-  Read10X(data.dir = "~/Documents/Project_scRNA_seq_meta_analysis/MetaAnalysis/RawFiles/GSE132880/Healthy228_out/filtered_gene_bc_matrices/mm10/")
Healthy_rep2 <- CreateSeuratObject(Healthy_rep2_data, project = "Healthy_rep2", assay = "RNA", min.cells = 3, min.features = 200)
Healthy_rep2 <- RenameCells(object = Healthy_rep2, new.names = paste0("Healthy_rep2_", Cells(x = Healthy_rep2)))
Healthy_rep2[["percent.mt"]] <- PercentageFeatureSet(Healthy_rep2, pattern = "^mt-")
# fix the metadata
Healthy_rep2@meta.data$age <- "Healthy"
Healthy_rep2@meta.data$species <- "Mouse"
Healthy_rep2@meta.data$rep_no <- 2
# Visualise QC metrics
png(filename = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/Healthyrep2QC.png", width = 600, height = 400)
VlnPlot(Healthy_rep2, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.2)
dev.off()
# Filtering of each dataset is based on the same cut off
Healthy_rep2 <- subset(Healthy_rep2, subset = nFeature_RNA > 200 & nFeature_RNA < 4500 & percent.mt < 20)
# calculate cell cycle score
Healthy_rep2 <- NormalizeData(Healthy_rep2) # normalisation required before cell cycle scoring
Healthy_rep2 <- CellCycleScoring(Healthy_rep2, s.features = s.genes$mouseGene, g2m.features = g2m.genes$mouseGene, set.ident = TRUE)
# Use scTransform to normalise datasets
Healthy_rep2 <- SCTransform(Healthy_rep2, vars.to.regress = c("percent.mt", "S.Score", "G2M.Score"))

Healthy_rep3_data <-  Read10X(data.dir = "~/Documents/Project_scRNA_seq_meta_analysis/MetaAnalysis/RawFiles/GSE132880/Healthy239_out/filtered_gene_bc_matrices/mm10/")
Healthy_rep3 <- CreateSeuratObject(Healthy_rep3_data, project = "Healthy_rep3", assay = "RNA", min.cells = 3, min.features = 200)
Healthy_rep3 <- RenameCells(object = Healthy_rep3, new.names = paste0("Healthy_rep3_", Cells(x = Healthy_rep3)))
Healthy_rep3[["percent.mt"]] <- PercentageFeatureSet(Healthy_rep3, pattern = "^mt-")
# fix the metadata
Healthy_rep3@meta.data$age <- "Healthy"
Healthy_rep3@meta.data$species <- "Mouse"
Healthy_rep3@meta.data$rep_no <- 3
# Visualise QC metrics
png(filename = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/Healthyrep3QC.png", width = 600, height = 400)
VlnPlot(Healthy_rep3, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.2)
dev.off()
# Filtering of each dataset is based on the same cut off
Healthy_rep3 <- subset(Healthy_rep3, subset = nFeature_RNA > 200 & nFeature_RNA < 4000 & percent.mt < 20)
# Calculate cell cycle score
# calculate cell cycle score
Healthy_rep3 <- NormalizeData(Healthy_rep3) # normalisation required before cell cycle scoring
Healthy_rep3 <- CellCycleScoring(Healthy_rep3, s.features = s.genes$mouseGene, g2m.features = g2m.genes$mouseGene, set.ident = TRUE) # Nek2 removed
Healthy_rep3 <- SCTransform(Healthy_rep3, vars.to.regress = c("percent.mt", "S.Score", "G2M.Score"))

Healthy_rep4_data <-  Read10X(data.dir = "~/Documents/Project_scRNA_seq_meta_analysis/MetaAnalysis/RawFiles/GSE132880/Healthy240_out/filtered_gene_bc_matrices/mm10/")
Healthy_rep4 <- CreateSeuratObject(Healthy_rep4_data, project = "Healthy_rep4", assay = "RNA", min.cells = 3, min.features = 200)
Healthy_rep4 <- RenameCells(object = Healthy_rep4, new.names = paste0("Healthy_rep4_", Cells(x = Healthy_rep4)))
Healthy_rep4[["percent.mt"]] <- PercentageFeatureSet(Healthy_rep4, pattern = "^mt-")
# fix the metadata
Healthy_rep4@meta.data$age <- "Healthy"
Healthy_rep4@meta.data$species <- "Mouse"
Healthy_rep4@meta.data$rep_no <- 4
# Visualise QC metrics
png(filename = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/Healthyrep4QC.png", width = 600, height = 400)
VlnPlot(Healthy_rep4, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.2)
dev.off()
# Filtering of each dataset is based on the same cut off
Healthy_rep4 <- subset(Healthy_rep4, subset = nFeature_RNA > 200 & nFeature_RNA < 4000 & percent.mt < 20)
# Calculate cell cycle score
# calculate cell cycle score
Healthy_rep4 <- NormalizeData(Healthy_rep4) # normalisation required before cell cycle scoring
Healthy_rep4 <- CellCycleScoring(Healthy_rep4, s.features = s.genes$mouseGene, g2m.features = g2m.genes$mouseGene, set.ident = TRUE) # Nek2 removed
Healthy_rep4 <- SCTransform(Healthy_rep4, vars.to.regress = c("percent.mt", "S.Score", "G2M.Score"))

# combine the QC data
qc_Healthy_rep1 <- Healthy_rep1@meta.data[, 1:5]
qc_Healthy_rep2 <- Healthy_rep2@meta.data[, 1:5]
qc_Healthy_rep3 <- Healthy_rep3@meta.data[, 1:5]
qc_Healthy_rep4 <- Healthy_rep4@meta.data[, 1:5]
qc <- rbind(qc_Healthy_rep1, qc_Healthy_rep2, qc_Healthy_rep3, qc_Healthy_rep4)

# use 'download as png' to save
plot_ly(qc, y = ~ nCount_RNA, color = ~ orig.ident, type = "box", colors = c("#383745","#A17724", "#9E9CC2", "#2A385B")) %>% layout(showlegend = F, autosize = F, width = 500, height = 500, xaxis = list(tickfont = list(size = 15), titlefont = list(size = 15)), yaxis = list(title = "nCount_RNA", tickfont = list(size = 15), titlefont = list(size = 15)), legend = list(font = list(size = 15)))

plot_ly(qc, y = ~ nFeature_RNA, color = ~ orig.ident, type = "box", colors = c("#383745","#A17724", "#9E9CC2", "#2A385B")) %>% layout(showlegend = F, autosize = F, width = 500, height = 500, xaxis = list(tickfont = list(size = 15), titlefont = list(size = 15)), yaxis = list(title = "nFeature_RNA", tickfont = list(size = 15), titlefont = list(size = 15)), legend = list(font = list(size = 15)))

plot_ly(qc, y = ~ percent.mt, color = ~ orig.ident, type = "box", colors = c("#383745","#A17724", "#9E9CC2", "#2A385B")) %>% layout(showlegend = F, autosize = F, width = 500, height = 500, xaxis = list(tickfont = list(size = 15), titlefont = list(size = 15)), yaxis = list(title = "percent.mt", tickfont = list(size = 15), titlefont = list(size = 15)), legend = list(font = list(size = 15)))
```
</div>

### Step 2 Integrate 4 replicates for Healthy.

All four datasets are now SCTransformed and the default assay is set to "SCT".

<div class = "teal">
```{r integrate_Healthy_replicates, warnings = FALSE, message = FALSE}
# select features for integration
options(future.globals.maxSize = 1500 * 1024^2) # it worked
Healthy_features <- SelectIntegrationFeatures(object.list = c(Healthy_rep1, Healthy_rep2, Healthy_rep3, Healthy_rep4), nfeatures = 3000)
Healthy_list <- PrepSCTIntegration(object.list = c(Healthy_rep1, Healthy_rep2, Healthy_rep3, Healthy_rep4), anchor.features = Healthy_features, verbose = FALSE) # error: exceeds the maximum allowed size of 500.00 MiB and adjust the limit to 1 GB in the previous line
# Identify the anchors - this step takes a while
Healthy_anchors <- FindIntegrationAnchors(object.list = Healthy_list, normalization.method = "SCT", anchor.features = Healthy_features, verbose = FALSE)
# Integrate data
Healthy_integrated <- IntegrateData(anchorset = Healthy_anchors, normalization.method = "SCT", verbose = FALSE) # this step reported the existence of duplicated cell names
## check duplicated cell names - 1 cell between rep1 and rep2 and 1 cell between rep2 and rep3 and need to remove these two cells from the datasets and redo the integration but NOT NOW, in a hurry
intersect(rownames(Healthy_rep1@meta.data), rownames(Healthy_rep2@meta.data))  
## [1] "ATTATTAAATCC"
intersect(rownames(Healthy_rep2@meta.data), rownames(Healthy_rep3@meta.data))  
## [1] "AGATCCTTACCC"
intersect(rownames(Healthy_rep3@meta.data), rownames(Healthy_rep4@meta.data))  
## character(0)
intersect(rownames(Healthy_rep1@meta.data), rownames(Healthy_rep3@meta.data))  
## character(0)
intersect(rownames(Healthy_rep1@meta.data), rownames(Healthy_rep4@meta.data))  
## character(0)
intersect(rownames(Healthy_rep2@meta.data), rownames(Healthy_rep4@meta.data))  
## character(0)
```
</div>

### Step 3 Proceed with downstream analysis on the integrated dataset

<div class = "teal">
```{r downstream_analysis, message = FALSE, warning = FALSE}
Healthy_integrated <- RunPCA(Healthy_integrated, verbose = FALSE)
set.seed(1024)
Healthy_integrated <- RunUMAP(Healthy_integrated, dims = 1:30)
saveRDS(Healthy_integrated, file = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated.rds")
png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_Integrated_UMAP_by_rep_no.png", res = 300, width = 2500, height = 2500)
DimPlot(Healthy_integrated, combine = FALSE, group.by = "rep_no", pt.size = 1)
dev.off()
png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_Integrated_UMAP_split_by_rep_no.png", res = 300, width = 7500, height = 2500)
DimPlot(Healthy_integrated, combine = FALSE, split.by = "rep_no", pt.size = 1)
dev.off()
```
</div>

### Step 4 FindNeighbors and FindClusters (on default assay which is "integrated")

<div class = "teal">
```{r clustering, message = FALSE, warning = FALSE}
Healthy_integrated <- FindNeighbors(Healthy_integrated, dims = 1:30)

for (i in 1:20) {
        Healthy_integrated <- FindClusters(Healthy_integrated, resolution = 0.1*i)
}
png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_clustree.png", res = 300, width = 4000, height = 3000)
clustree(Healthy_integrated) # cluster tree visualisation
dev.off()
png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_clustree_stability.png", res = 300, width = 4000, height = 3000)
clustree(Healthy_integrated, node_colour = "sc3_stability") # cluster tree visualisation
dev.off()

# It seems resolution 0.8 is a good choice and change the clusters to the res 0.8 one
Healthy_integrated@meta.data$seurat_clusters <- Healthy_integrated@meta.data$integrated_snn_res.0.8
Healthy_integrated <- FindClusters(Healthy_integrated, resolution = 0.8) # run it again

png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_clustering_Healthy_integrated.png", res = 300, width = 2500, height = 2500)
DimPlot(Healthy_integrated, label = TRUE, label.size = 6) + NoLegend()
p <- DimPlot(Healthy_integrated, label = TRUE, label.size = 6) + NoLegend()
ggplotly(p, width = 500, height = 500)
dev.off()

# Find cluster markers using the clustering information in this assay
Healthy_integrated_markers <- FindAllMarkers(Healthy_integrated, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
Healthy_integrated_markers_top10 <- Healthy_integrated_markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)
write.csv(Healthy_integrated_markers_top10, file = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_cluster_marker_top10.csv")
# Use topGO to annotate the cluster markers
# need to install BiocManager::install("org.Mm.eg.db") if not already
## cluster 0 is done first - build a loop to get all clusters' GO
length <- length(unique(Healthy_integrated@meta.data$seurat_clusters)) # number of loops
for (i in 0:(length - 1)) { # starting from 0
        cluster <- subset(Healthy_integrated, idents = as.character(i))
        expr <- cluster@assays$integrated@data
        # Select genes that are expressed > 0 in at least 75% of cells (somewhat arbitrary definition and too high in my case)
        n.gt.0 <- apply(expr, 1, function(x)length(which(x > 0)))
        expressed.genes <- rownames(expr)[which(n.gt.0/ncol(expr) >= 0.60)]
        all.genes <- rownames(expr)
        # define geneList as 1 if gene is in expressed.genes, 0 otherwise
        geneList <- ifelse(all.genes %in% expressed.genes, 1, 0)
        names(geneList) <- all.genes
        # Create topGOdata object
        GOdata <- new("topGOdata",
                      ontology = "BP", # use biological process ontology
                      allGenes = geneList,
                      geneSelectionFun = function(x)(x == 1),
                      annot = annFUN.org, mapping = "org.Mm.eg.db", ID = "symbol")
        # Test for enrichment using Fisher's Exact Test
        resultFisher <- runTest(GOdata, algorithm = "elim", statistic = "fisher")
        GO_table <- GenTable(GOdata, Fisher = resultFisher, topNodes = 20, numChar = 60)
        # Save GO table
        write.csv(GO_table, file = paste0("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_cluster_", i,"GO_term_table", ".csv"))
        # Generate GO term bar graph
        Go_table_touse <- GO_table[1:5, ] # choose the top 5 GO terms
        Go_table_touse$NewTerm <- paste0(Go_table_touse$GO.ID, "_", Go_table_touse$Term)
        Go_table_touse$P_value <- -log10(as.numeric(Go_table_touse$Fisher))
        colour_touse <- hue_pal()(length)[i+1]
        png(paste0("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_cluster_", i,"GO_term_table", ".png"), res = 300, width = 4000, height = 1000)
        print(ggplot(Go_table_touse, aes(x = NewTerm, y = P_value)) +
                geom_bar(stat="identity", fill = colour_touse, width = 0.6) + 
                coord_flip() +
                ggtitle(paste0("Adult Healthy Cluster ", i)) +
                ylab(expression("-log"[10]~ paste("(", italic(P), " value)"))) +
                theme_classic() + 
                theme(axis.line = element_line(colour = "black", size = 1, linetype = "solid"), axis.text.x = element_text(face = "bold", color = "black", size = 14), axis.text.y = element_text(face="bold", color = "black", size = 14), axis.title.y = element_blank(), plot.title = element_text(size = 14, face = "bold"), axis.title.x = element_text(color = "black", size = 14, face = "bold"))) # Remember to wrap the png call using print to get it plotted and saved!!!!!!!!
        dev.off()
}
```
</div>

### Step 5 Change default assay to "SCT"; normalize then generate FeaturePlots 

The reason of changing back to RNA assay is because the integrated assay only has 3000 genes and values from SCT assay represent the SCT normalized values for each dataset, prior to integration.

<div class = "teal">
```{r feature_plot, warning = FALSE, message = FALSE}
DefaultAssay(object = Healthy_integrated) <- "RNA"
png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_RNAassay_Pecam1_feature_plot.png", res = 300, width = 2500, height = 2500)
FeaturePlot(Healthy_integrated, features = c("Pecam1"), cols = c("lightgrey", "#003333"), pt.size = 1)
p <- FeaturePlot(Healthy_integrated, features = c("Pecam1"), cols = c("lightgrey", "#003333"), pt.size = 1)
ggplotly(p, width = 500, height = 500)
dev.off()
```
</div>

### Step 6 Extract Endothelial cells using AUCell

<div class = "teal">
```{r feature_plot, warning = FALSE, message = FALSE}
saveRDS(Healthy_integrated, "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_object.rds") # save object 
# Load count data
exprMatrix <- Healthy_integrated@assays$RNA@counts
exprMatrix <- as.matrix(exprMatrix) # convert sparse matrix to matrix
dim(exprMatrix)
# Set gene set
ECgenes <- c("Pecam1", "Itgb1", "Cd34", "Cd36", "Entpd1", "Cd44", "Cd47", "Icam1", "Itgb3", "Selplg", "Cd80", "Cd86", "Cd93", "Icam2", "Eng", "Vcam1", "Il1r1", "Thbd", "F3", "Ace", "Cdh5", "Mcam", "Bsg", "Cd151", "Cd160", "Pik3cd", "Procr", "Il13ra1", "Cd248", "Kdr", "Adam8", "Adam9", "Adam10", "Adam12", "Adam15", "Adam17", "Adam33", "Adamts13", "Adamts18", "Cxcl16", "Dcbld2", "Emcn", "Esam", "Itga4", "Klf4")
geneSets <- GeneSet(ECgenes, setName = "endothelial_cells")
geneSets
# Build gene expression rankings for each cell
cells_rankings <- AUCell_buildRankings(exprMatrix, nCores = 2, plotStats = TRUE)
cells_rankings
save(cells_rankings, file = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_EC_rankings.RData")
# Calculate enrichment for the gene signatures (AUC)
cells_AUC <- AUCell_calcAUC(geneSets, cells_rankings) # add AUC score to the Healthy_integrated object
DefaultAssay(object = Healthy_integrated) <- "integrated"
Healthy_integrated@meta.data$AUC_score <- t(getAUC(cells_AUC))
save(cells_AUC, file = "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_EC_AUC.RData")
# Determine the cells with the given gene signatures or active gene sets
set.seed(123)
cells_assignment <- AUCell_exploreThresholds(cells_AUC, plotHist = TRUE, assign = TRUE)
cells_assignment # "The AUC might follow a normal distribution (random gene-set?).  The global distribution overlaps the partial distributions." Very good to see that the FACS is appreciated by the AUCell protocol
cells_assignment$endothelial_cells$aucThr$thresholds

endoAssigned <- cells_assignment$endothelial_cells$assignment
length(endoAssigned)

geneSetName <- rownames(cells_AUC)[grep("endothelial_cells", rownames(cells_AUC))]
png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_AUCell_EC_hist.png", res = 300, width = 1500, height = 1500)
AUCell_plotHist(cells_AUC[geneSetName, ], aucThr = cells_assignment$endothelial_cells$aucThr$thresholds[4, 1])
abline(v = cells_assignment$endothelial_cells$aucThr$thresholds[4, 1])
dev.off()

# AUCscore as feature plot
p <- FeaturePlot(Healthy_integrated, features = "AUC_score", cols = viridis::viridis(21)) + NoLegend()
ggplotly(p, width = 500, height = 500)

png("~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_integrated_RNAassay_AUCell_EC.png", res = 300, width = 2750, height = 2500)
DimPlot(Healthy_integrated, cells.highlight = WhichCells(object = Healthy_integrated, expression = AUC_score > cells_assignment$endothelial_cells$aucThr$thresholds[4, 1])) + scale_color_manual(labels = c("non-EC", "EC"), values = c("grey", "red")) + labs(color = "Cell type")
p <- DimPlot(Healthy_integrated, cells.highlight = WhichCells(object = Healthy_integrated, expression = AUC_score > cells_assignment$endothelial_cells$aucThr$thresholds[4, 1]), sizes.highlight = NULL, cols.highlight = "red") + labs(title = "Endothelial Cell Assignment") + NoLegend() + theme(plot.title = element_text(hjust = 0.5))
ggplotly(p, width = 500, height = 500)
dev.off()

# Subset and store the EC data - the AUCell package can't assign cells as it's a pretty good normal distribution and I will just save all the cells.
Healthy_EC <- subset(Healthy_integrated, cells = names(which(getAUC(cells_AUC)["endothelial_cells",] > cells_assignment$endothelial_cells$aucThr$thresholds[4, 1])))
saveRDS(Healthy_EC, "~/Documents/Project_scRNA_seq_meta_analysis/P6_P10_Adult_Healthy_mouse_meta/GSE132880_Healthy_EC.rds")
```
</div>
