---
title: "GSE136088_2WSham_Adult"
author: "Cass Li"
date: "23/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
div.teal pre { background-color:#fff44f; }
div.teal pre.r { background-color:#b2d8d8; }
</style>

### Step 1 Load libraries

<div class = "teal">
```{r library_loading, message = FALSE, warning = FALSE}
# load libraries
library(Seurat)
library(ggplot2)
library(homologene)
library(clustree)
library(dplyr)
library(topGO)
library(org.Mm.eg.db)
library(scales)
library(GSEABase)
library(AUCell)
library(grid)
library(tibble)
library(monocle)
library(Biobase)
library(scrat)
library(plotly)
library(scran)
library(GENIE3)
library(RcisTarget)
# library(monocle3)
```
</div>

Acute myocardial infarction (MI) was modeled in C57BL6/J wild type (WT) 8-10-week-old male mice (The Jackson Laboratories and confirmed via echocardiographic analysis, similar to previously described (Duan, et al., 2017). A left thoracotomy was performed via the fourth intercostal space and the lungs retracted to expose the heart. After opening the pericardium, the left anterior descending coronary artery was ligated with 7-0 silk suture approximately 2 mm below the edge of the left atrial appendage. Ligation was considered successful when the anterior wall of the left ventricle turned pale. The lungs were inflated by increasing positive end-expiratory pressure and the thoracotomy site closed in layers with 6-0 suture. Animals were maintained on a 37 °C heating pad until recovery and for 2 h after surgery. Another group of mice underwent sham ligation, with a similar surgical procedure without tightening the suture around the coronary artery. Mice with an estimated pressure gradient across the aortic constriction below 40 mmHg were not included in the experiments. Hearts were collected at 14 days post-Sham surgery (***n = 4, pooled***) or MI (n=1), perfused with ice-cold PBS to remove red blood cells followed by perfusion with 50 mM KCl to arrest the heart in diastole and then fixed for 4 hours in freshly prepared 4% PFA at 4°C, rinsed with PBS and cryoprotected in 30% sucrose/PBS overnight before embedding in OCT (Tissue-Tek). DropSeq was performed as previously described (Macosko, et al., 2015). The quantity and quality of cDNA was measured using an Agilent Bioanalyzer hsDNA chip. To generate a library cDNA was fragmented and amplified (12 cycles) using the Nextera XT DNA Sample prep kit with three separate reactions of 600, 1,200 and 1,800 pg input cDNA.
The quantity and quality of cDNA was measured using an Agilent Bioanalyzer hsDNA chip. To generate a library cDNA was fragmented and amplified (12 cycles) using the Nextera XT DNA Sample prep kit with three separate reactions of 600, 1,200 and 1,800 pg input cDNA. The libraries were pooled and purified twice using 0.7X volume of SPRIselect beads. The purified libraries were quantified using an hsDNA chip and were sequenced on an Illumina HiSeq 2500 using the sequencing parameters described in the DropSeq protocol. DropSeq was performed as previously described (Macosko et al., 2015).

### Step 2 Load datasets for Sham.

<div class = "teal">
```{r cache = TRUE}
Sham_data <- read.delim("~/Documents/Project_scRNA_seq_meta_analysis/GSE136088/GSE136088_RAW/GSM4040775_Sham-out_gene_exon_tagged.dge.txt.gz")
Sham_data_1 <- Sham_data[, -1]
rownames(Sham_data_1) <- Sham_data[, 1]
Sham <- CreateSeuratObject(counts = Sham_data_1, project = "GSE136088_Sham", assay = "RNA", min.cells = 3, min.features = 200)
Sham[["percent.mt"]] <- PercentageFeatureSet(Sham, pattern = "^mt-")

# fix the metadata
Sham@meta.data$age <- "Adult" # 8 to 10 weeks
Sham@meta.data$species <- "Mouse"
Sham@meta.data$condition <- "2W_Sham"
Sham@meta.data$group <- paste0(Sham@meta.data$condition, " ", Sham@meta.data$species)

# Visualise QC metrics
png(filename = "ShamQC.png", width = 600, height = 400)
VlnPlot(Sham, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0.2)
dev.off()

# Filtering of each dataset is based on the same cut off
Sham <- subset(Sham, subset = nFeature_RNA > 200 & nFeature_RNA < 4000 & percent.mt < 20)

# Calculate cell cycle scores - these are human genes and can't be used directly. Use homologene package to solve the problem
s.genes <- human2mouse(cc.genes$s.genes) # return a dataframe
g2m.genes <- human2mouse(cc.genes$g2m.genes) # return a dataframe
Sham <- NormalizeData(Sham) # normalise before cell cycle score
Sham <- CellCycleScoring(Sham, s.features = s.genes$mouseGene, g2m.features = g2m.genes$mouseGene, set.ident = TRUE)
# Use scTransform to normalise datasets
Sham <- SCTransform(Sham, vars.to.regress = c("percent.mt", "S.Score", "G2M.Score")) # default assay is now set to SCT

# combine the QC data
qc <- Sham@meta.data[, 1:9]

# use 'download as png' to save
plot_ly(qc, y = ~ nCount_RNA, color = ~ condition, type = "box", colors = c("#383745","#A17724", "#9E9CC2"), width = 200, height = 500) %>% layout(showlegend = F, autosize = F, xaxis = list(title = "E-MTAB-7376", tickfont = list(size = 15), titlefont = list(size = 15)), yaxis = list(title = "nCount_RNA", tickfont = list(size = 15), titlefont = list(size = 15)), legend = list(font = list(size = 15)))

plot_ly(qc, y = ~ nFeature_RNA, color = ~ condition, type = "box", colors = c("#383745","#A17724", "#9E9CC2"), width = 200, height = 500) %>% layout(showlegend = F, autosize = F, xaxis = list(title = "E-MTAB-7376", tickfont = list(size = 15), titlefont = list(size = 15)), yaxis = list(title = "nFeature_RNA", tickfont = list(size = 15), titlefont = list(size = 15)), legend = list(font = list(size = 15)))

plot_ly(qc, y = ~ percent.mt, color = ~ condition, type = "box", colors = c("#383745","#A17724", "#9E9CC2"), width = 200, height = 500) %>% layout(showlegend = F, autosize = F, xaxis = list(title = "E-MTAB-7376", tickfont = list(size = 15), titlefont = list(size = 15)), yaxis = list(title = "percent.mt", tickfont = list(size = 15), titlefont = list(size = 15)), legend = list(font = list(size = 15)))
```
</div>

### Step 3 Dimension reduction and clustering of each dataset

<div class = "teal">
```{r downstream_analysis, message = FALSE, warning = FALSE}
# Sham 2W
# dimension reduction
Sham <- RunPCA(Sham, verbose = FALSE)
set.seed(1024)
Sham <- RunUMAP(Sham, dims = 1:30)
saveRDS(Sham, file = "Sham.rds")

png("Sham_UMAP.png", res = 300, width = 2500, height = 2500)
DimPlot(Sham, combine = FALSE, pt.size = 1)
dev.off()

# find neighbours
Sham <- FindNeighbors(Sham, dims = 1:30)

for (i in 1:20) {
        Sham <- FindClusters(Sham, resolution = 0.1*i)
}

png("Sham_clustree.png", res = 300, width = 4000, height = 3000)
clustree(Sham) # cluster tree visualisation
dev.off()

png("Sham_clustree_stability.png", res = 300, width = 4000, height = 3000)
clustree(Sham, node_colour = "sc3_stability") # cluster tree visualisation
dev.off()

# It seems resolution 0.6 is a good choice and change the clusters to the res 0.6 one
Sham <- FindClusters(Sham, resolution = 0.6) # this resolution is difficult to determine and the package "clustree" is used to help with all resolution between 0.1 and 2 (with a step of 0.1) tested
Sham@meta.data$seurat_clusters <- Sham@meta.data$SCT_snn_res.0.6

png("Sham_clustering.png", res = 300, width = 2500, height = 2500)
DimPlot(Sham, label = TRUE, label.size = 6) + NoLegend()
p <- DimPlot(Sham, label = TRUE, label.size = 6) + NoLegend()
ggplotly(p, width = 500, height = 500)
dev.off()

# Find top markers
Sham_markers <- FindAllMarkers(Sham, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
Sham_markers_top10 <- Sham_markers %>% group_by(cluster) %>% top_n(n = 10, wt = avg_logFC)
write.csv(Sham_markers_top10, file = "Sham_cluster_marker_top10.csv")

# Use topGO to annotate the cluster markers
# need to install BiocManager::install("org.Mm.eg.db") if not already
## cluster 0 is done first - build a loop to get all clusters' GO
length <- length(unique(Sham@meta.data$seurat_clusters)) # number of loops
for (i in 0:(length - 1)) { # starting from 0
        cluster <- subset(Sham, idents = as.character(i))
        expr <- cluster@assays$SCT@data
        # Select genes that are expressed > 0 in at least 75% of cells (somewhat arbitrary definition and too high in my case)
        n.gt.0 <- apply(expr, 1, function(x)length(which(x > 0)))
        expressed.genes <- rownames(expr)[which(n.gt.0/ncol(expr) >= 0.60)]
        all.genes <- rownames(expr)
        # define geneList as 1 if gene is in expressed.genes, 0 otherwise
        geneList <- ifelse(all.genes %in% expressed.genes, 1, 0)
        names(geneList) <- all.genes
        # Create topGOdata object
        GOdata <- new("topGOdata",
                      ontology = "BP", # use biological process ontology
                      allGenes = geneList,
                      geneSelectionFun = function(x)(x == 1),
                      annot = annFUN.org, mapping = "org.Mm.eg.db", ID = "symbol")
        # Test for enrichment using Fisher's Exact Test
        resultFisher <- runTest(GOdata, algorithm = "elim", statistic = "fisher")
        GO_table <- GenTable(GOdata, Fisher = resultFisher, topNodes = 20, numChar = 60)
        # Save GO table
        write.csv(GO_table, file = paste0("Sham_cluster_", i,"GO_term_table", ".csv"))
        # Generate GO term bar graph
        Go_table_touse <- GO_table[1:5, ] # choose the top 5 GO terms
        Go_table_touse$NewTerm <- paste0(Go_table_touse$GO.ID, "_", Go_table_touse$Term)
        Go_table_touse$P_value <- -log10(as.numeric(Go_table_touse$Fisher))
        colour_touse <- hue_pal()(length)[i+1]
        png(paste0("Sham_cluster_", i,"GO_term_table", ".png"), res = 300, width = 4000, height = 1000)
        print(ggplot(Go_table_touse, aes(x = NewTerm, y = P_value)) +
                geom_bar(stat = "identity", fill = colour_touse, width = 0.6) + 
                coord_flip() +
                ggtitle(paste0("Sham 2W cluster ", i)) +
                ylab(expression("-log"[10]~ paste("(", italic(P), " value)"))) +
                theme_classic() + 
                theme(axis.line = element_line(colour = "black", size = 1, linetype = "solid"), axis.text.x = element_text(face = "bold", color = "black", size = 14), axis.text.y = element_text(face = "bold", color = "black", size = 14), axis.title.y = element_blank(), plot.title = element_text(size = 14, face = "bold"), axis.title.x = element_text(color = "black", size = 14, face = "bold"))) # Remember to wrap the png call using print to get it plotted and saved!!!!!!!!
        dev.off()
}

saveRDS(Sham, "Sham.rds")

png("Sham_Pecam1_feature_plot.png", res = 300, width = 2500, height = 2500)
FeaturePlot(Sham, features = c("Pecam1"), cols = c("lightgrey", "#003333"), pt.size = 1)
p <- FeaturePlot(Sham, features = c("Pecam1"), cols = c("lightgrey", "#003333"), pt.size = 1)
ggplotly(p, width = 500, height = 500)
dev.off()

# Extract endothelial cells
# Load count data
exprMatrix <- Sham@assays$SCT@data
exprMatrix <- as.matrix(exprMatrix) # convert sparse matrix to matrix
dim(exprMatrix)
# Set gene set
ECgenes <- c("Pecam1", "Itgb1", "Cd34", "Cd36", "Entpd1", "Cd44", "Cd47", "Icam1", "Itgb3", "Selplg", "Cd80", "Cd86", "Cd93", "Icam2", "Eng", "Vcam1", "Il1r1", "Thbd", "F3", "Ace", "Cdh5", "Mcam", "Bsg", "Cd151", "Cd160", "Pik3cd", "Procr", "Il13ra1", "Cd248", "Kdr", "Adam8", "Adam9", "Adam10", "Adam12", "Adam15", "Adam17", "Adam33", "Adamts13", "Adamts18", "Cxcl16", "Dcbld2", "Emcn", "Esam", "Itga4", "Klf4")
geneSets <- GeneSet(ECgenes, setName = "endothelial_cells")
geneSets

# Build gene expression rankings for each cell
detectCores()
cells_rankings <- AUCell_buildRankings(exprMatrix, nCores = 2, plotStats = TRUE)
cells_rankings
save(cells_rankings, file = "Sham_EC_rankings.RData")
# Calculate enrichment for the gene signatures (AUC)

cells_AUC <- AUCell_calcAUC(geneSets, cells_rankings) 
# add AUC score to the Sham object
Sham@meta.data$AUC_score <- t(getAUC(cells_AUC))
save(cells_AUC, file = "Sham_EC_AUC.RData")

# Determine the cells with the given gene signatures or active gene sets
set.seed(123)
cells_assignment <- AUCell_exploreThresholds(cells_AUC, plotHist = TRUE, assign = TRUE)
cells_assignment$endothelial_cells$aucThr$thresholds

endoAssigned <- cells_assignment$endothelial_cells$assignment
length(endoAssigned) # 1026

geneSetName <- rownames(cells_AUC)[grep("endothelial_cells", rownames(cells_AUC))]
png("Sham_AUCell_EC_hist.png", res = 300, width = 1500, height = 1500)
AUCell_plotHist(cells_AUC[geneSetName, ], aucThr = cells_assignment$endothelial_cells$aucThr$thresholds[2, 1])
abline(v = cells_assignment$endothelial_cells$aucThr$thresholds[2, 1])
dev.off()

# AUCscore as feature plot
p <- FeaturePlot(Sham, features = "AUC_score", cols = viridis::viridis(21)) + NoLegend()
ggplotly(p, width = 500, height = 500)

png("Sham_AUCell_EC.png", res = 300, width = 2750, height = 2500)
DimPlot(Sham, cells.highlight = WhichCells(object = Sham, expression = AUC_score > cells_assignment$endothelial_cells$aucThr$thresholds[2, 1])) + scale_color_manual(labels = c("non-EC", "EC"), values = c("grey", "red")) + labs(color = "Cell type")
p <- DimPlot(Sham, cells.highlight = WhichCells(object = Sham, expression = AUC_score > cells_assignment$endothelial_cells$aucThr$thresholds[2, 1]), sizes.highlight = NULL, cols.highlight = "red") + labs(title = "Endothelial Cell Assignment") + NoLegend() + theme(plot.title = element_text(hjust = 0.5))
ggplotly(p, width = 500, height = 500)
dev.off()

# Subset and store the EC data
Sham_EC <- subset(Sham, cells = names(which(getAUC(cells_AUC)["endothelial_cells",] > cells_assignment$endothelial_cells$aucThr$thresholds[2, 1])))
saveRDS(Sham_EC, "Sham_EC.rds")
```
</div>
